\chapter{LITERATURE REVIEW}
A robot may define as an electro-mechanical device, which
is capable of sensing its surrounding and taking its decision
(command).In general, robot must be able to move (by
mechanical movement), it must be able to sense (by
transducer) and it should be take decision (by remote
control or artificial intelligence). A robotic arm is a robot
manipulator, which can perform similar functions to a
human arm.
Robotics arm is vital role of industrial application. Most
robotics arm perform the task such as welding, trimming,
picking, placing and painting etc \cite{r1}.

Some    basic    applications    of    robots    utilizing    voice recognition  are  to  support  elderly  people  or  people  with disability,  voice  controlled  personal  assistance  etc . The   Raspberry   pi   board   has   several   applications,   from distance measurement of a target object from another object for  the  purpose  of  civil  engineering  to  developing  a robotic arm to help medical staff and elderly people. Instead of   using   multiple   dynamic   interfaces,it   is   easier   to communicate with machines through voice commands\cite{r2}.

Raspberry Pi is a series of small single-board computers developed  in  the  United  Kingdom  by  the  Raspberry  Pi Foundation in association with Broadcom. The Raspberry Pi is   a   lightweight,   powerful,   inexpensive,   hackable,   and educational  computer board  .  The  Raspberry  Pi was  introduced  in  2012,  and  several  versions  and  variants have  since  been  released.  The  original  Raspberry  Pi  had  a single-core  700MHz  CPU  and  just  256MB  RAM,  and  a quad-core 1.4GHz CPU with 1GB RAM is available for the new  edition.  For  Raspberry  Pi,  the  main  price  point  has always  been  \$ 35,and  all  models  have  been  \$35  or  less, including the Pi Zero, which is just \$5 .Some of these  devices  are  necessary,  others  are  optional,  but  all Raspberry Pi models have the same BCM2835 CPU, which is  inexpensive,  efficient,  and  does  not  consume  a  lot  of energy. The Raspberry Pi also utilizes an operating system like any other computer. In  order  to  learn  programming  skills,  create  hardware projects,   do   home   automation   and   even   use   them   in industrial   applications,   people   all   over   the   world   use Raspberry   Pi.   There   have   been   three   generations   of Raspberry  Pi`s:  Pi  1,  Pi  2,  and  Pi  3,  and  most  generations have  usually had a  Model  A and a  Model  B. Model  A  is a cheaper version which appears to have lower RAM and USB and  Ethernet  ports.  The  Pi  Zero  is  a  spinoff,  made  much smallerand cheaper, of the original (Pi 1) generation. Table I provides a comparison of the scale, weight, and cost of the standard Raspberry Pi generation\cite{r2}.

Computer  vision  and  artificial  intelligence  have  been successfully  utilized  to  operate  complex  robotic  systems  in many  works. For instance, in a recent work , the authors designed  an  automatedrobotic  arm-based  assistance deviceby employingsimple   stereo   matching   and   q-learning optimization  techniques.  The  proposed  device  can  perform five degrees of operation in a single instance and detect any object with the help of stereo vision. The system also keeps track  of  an  object's  parameters.  The  stereo  camera  can identify   the   RGB   color.   In   this   work,   the   Q-learningframework is  employed  to  control  the  position  of  the robot’s   arm.   Finally,   the   paper   showed   experiments   to identify  an  object's  stereo  vision  and  feature  point.  The downfall  of  the  study  is  that  it  did  not  specify  the  exact distance between the objects \cite{r3}.

Both the purpose of optimizing today's industrial production and integrating various
technologies is the goal of Industry 4.0. Thus, it is critically important issue to integrate the
information system with the information in the real space through the Internet, such as, the
IoT (Internet of Things), big data, AI (artificial intelligence) and other diverse customized
manufacturing. A single-function target is adopted in traditional industrial manufacturing with
most of the mechanical arms. The advantage of combine with integrated system of complete
work is that they can complete quick and accurately to pick an objects and to move to a
suitable place at the same time. Such behavior can reduce the time for complicating the
operations convenience, and also totally improve the allocation of human resources .
However, under the influence of globalization in order to apply those substantial monitoring
records from the process of production, to make more advanced technical planning with the
assistance of high technique is necessary. The consideration to apply an auxiliary tool that can
bring huge profits to the enterprise, apply precise robotic arms maximizes the usage of all
machine equipments in the factory, and even to monitor the signal for handling the production
of components in the factory are some most strategies carried out in a factor. Especially, if an
enterprise is trying to transform the flow of manufacturing. Record and report timely to
information are importantly required, such as storage, storage location, management
personnel, etc., and effectively predict the loss of the machine, fault maintenance, and even
reduce operating costs caused by misjudgment. Moreover, how to embed human thinking and
behavior capabilities into a robots let it becomes smarter, more agile, and even low-cost,
which is worth thinking. It is possible to establish a new model of cooperation between the
human and machine. Under the cooperation of man and machine, robots can not only help
humans complete cumbersome and dangerous special tasks, but also transmit the lowest-level
information .\cite{r4}.

In today’s world, time and man power are important constraints for the completion of tasks. Robots are used in
industries to perform simple repetitive tasks. Compared to humans, robots complete tasks faster and with greater accuracy.
They are increasingly used in industries to automate tasks in an assembly line for pick and place. Robot arms are used as a
pick and place robot in industries. This paper presents a robot arm used as a pick and place robot using a raspberry pi
microcontroller. The robot arm can automatically move to a location where the object to be lifted and placed. Ultrasonic
distance sensors are installed at the robot arm to recognize the object. The robot arm is used to hold the object and move it to
desired destination.\cite{r5}